Fire Safety Regulation Violations in Toronto Residential Properties: Analysis by Property Type and Inspection Duration

### 2024-12-04 paper/paper.qmd
Updated final completed version of paper

- $\text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right)$ represents the log-odds of $p_i$.
- $\beta_0$ is the intercept term of the Bayesian logistic regression, representing the baseline log-odds of a violation when $date = 0$ and 'type' is the reference category. Formula (2) specifies that $\beta_0$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.
- $\beta_1$ is the coefficient for predictor variable 'date', representing the change in log-odds of a violation for per unit increase in 'date', i.e., the inspection time interval. Formula (3) specifies that $\beta_1$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.
- $\beta_2$ is the coefficient for the predictor variable 'type', representing the change in log-odds of a violation for each unit increase in 'type'. Formula (4) specifies that $\beta_2$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.

@@

The table firstly lists estimates of coefficients for all parameters. The first line suggests an intercept of -6.72 for the model, indicating very low baseline odds of a violation for the reference property type when $date = 0$. The second line shows that the estimated coefficient for predictor 'date' is 0.02, which is very small and suggests that the inspection duration has a negligible effect on the violation outcome of observations.

>>>>

- $\text{logit}(p_i) = \log\left(\frac{p_i}{1 - p_i}\right)$ represents the log-odds of $p_i$.
- $\beta_0$ is the intercept term of the Bayesian logistic regression, representing the baseline log-odds of a violation when $\text{date} = 0$ and 'type' is the reference category. Formula (2) specifies that $\beta_0$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.
- $\beta_1$ is the coefficient for predictor variable 'date', representing the change in log-odds of a violation for per unit increase in 'date', i.e., the inspection time interval. Formula (3) specifies that $\beta_1$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.
- $\beta_2$ is the coefficient for the predictor variable 'type', representing the change in log-odds of a violation for each unit increase in 'type'. Formula (4) specifies that $\beta_2$ follows normal distribution with a mean of 0 and a variance of $2.5^2$.

@@

The table firstly lists estimates of coefficients for all parameters. The first line suggests an intercept of -6.72 for the model, indicating very low baseline odds of a violation for the reference property type when $\text{date} = 0$. The second line shows that the estimated coefficient for predictor 'date' is 0.02, which is very small and suggests that the inspection duration has a negligible effect on the violation outcome of observations.
